The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-13 Manuscript/Response_To_Comments.tex

 We thank the reviewer for being appreciative and understanding of the 
 good motivations driving this paper. We agree that a deeper discussion 
 of why home-court advantage would not exist in the bubble would be beneficial 
 to setting up the paper. We added in a discussion of why all the different 
 factors play into creating home-court advantage and how each one may or may 
 not still exist in the bubble. This addition to the paper can be found in the first paragraph
 of the Introduction section. For the most part, these factors disappeared 
 in the context of the bubble, except travel/time and miles for reasons we
 discuss in the paper.

\begin{comment}
Also, this paper https://arxiv.org/abs/1701.05976 finds that altitude matters
(Colorado and Utah teams have the highest home advantage in multiple sports),
so that could be added/discussed. So changes in home advantage in the bubble
could impact teams differently, and NBA teams Nuggets and Jazz could be hurt
more than other teams since they no longer benefit from an altitude advantage.
\end{comment}

 We are very grateful that referee~2 brought \citet{Lopez} to our attention. 
 It was added to Literature Review(at the end of the third paragraph) and
 discussed in the Introduction(first paragraph) when setting 
 up and explaining the factors that would be missing from normal home-court 
 advantage when playing in the NBA bubble. The most noteworthy point added 
 from this paper, as pointed out by referee~2, was the evidence supporting 
 geographic factors impact home-court advantage. Particularly, teams like 
 the Utah Jazz and Denver Nuggets are the NBA teams who would benefit from 
 the high-altitude effects. This is discussed in more detail in the manuscript.
  Also, a few other references were added to strengthen the paper.
  First, \cite{Price} discuss empirical evidence in favor of referee bias towards
  home teams. Second, \cite{Jones} analyzes the effects of home-court advantage
  as component parts and how the effects of home-court advantage impact each 
  individual quarter of play. Lastly, \cite{Boudreaux} uses a natural
  experiment to estimate how the crowd effect of home-court advantage impacts winning.

### 2022-02-13 Manuscript/manuscript.tex
Update manuscript.tex

It's worth noting that much of this paper discusses the effects from an
offensive point of view, focusing on a team's ability to score. However, one of 
the main factors that affects an offense's ability to score is the opposing
defense. It's possible that home-court advantage mainly functions as an extra
defender for home teams, which is how it negatively impacts away scoring. There
is not much home fans can do to help their team on offense, except being quiet
so players can easily communicate and focus. However, when on defense, fans can
act as a "sixth defender" supporting their team by cheering loudly and making it
harder on the offense. Also, as seen in the study \cite{Price}, fans can 
create turnovers by pressuring officials to make calls in their favor.  
This would explain how away teams were able to improve
offensively in the bubble. Home teams did not have the regular help from the
noise of fans that hinders the away team's offensive efforts. This would also
explain why home team offense didn't show significant change in the bubble, the
in-game offensive environment was largely unaltered for home teams since the
bubble provided the same quiet environment they're used to at home while on
offense. I still believe home-court advantage is better categorized as a
negative effect on away team offense, since it's more likely
noise from fans lowers level of play of away offense rather than raises the level
of play of home defense. This will be further discussed below.

@@

\jy{are you interested in phd in statistics?}

>>>>

It's worth noting that much of this paper discusses the effects from an
offensive point of view, focusing on a team's ability to score. However, one of 
the main factors that affects an offense's ability to score is the opposing
defense. It's possible that home-court advantage mainly functions as an extra
defender for home teams, which is how it negatively impacts away scoring. There
is not much home fans can do to help their team on offense, except being quiet
so players can easily communicate and focus. However, when on defense, fans can
act as a ``''sixth defender''`` supporting their team by cheering loudly and making it
harder on the offense. Also, as seen in the study \cite{Price}, fans can 
create turnovers by pressuring officials to make calls in their favor.  
This would explain how away teams were able to improve
offensively in the bubble. Home teams did not have the regular help from the
noise of fans that hinders the away team's offensive efforts. This would also
explain why home team offense didn't show significant change in the bubble, the
in-game offensive environment was largely unaltered for home teams since the
bubble provided the same quiet environment they're used to at home while on
offense. I still believe home-court advantage is better categorized as a
negative effect on away team offense, since it's more likely
noise from fans lowers level of play of away offense rather than raises the level
of play of home defense. This will be further discussed below.

@@
